WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-10 paper/ms.tex
Update ms.tex

\title{The Early Arrival of WASP-4\lowercase{b}}

@@

\begin{abstract}
  %TODO: final numbers
  Combining data from the Transiting Exoplanet Survey Satellite (TESS)
  with previous studies, we show that the transit times of WASP-4b are
  incompatible with a constant orbital period.  In particular, the
  transits seem to have arrived $77.8 \pm 10.8$ seconds early, and the
  period appears to be shrinking by $\dot{P}=-12.1 \pm 1.2$
  milliseconds per year.   From TESS observations of WASPs-6b, -18b,
  and -46b, we show that a systematic offset between the TESS times
  and the barycentric reference sufficient to explain WASP-4b is ruled
  out at 6.3$\sigma$.  The timing variations seem to be astrophysical,
  and could be caused by apsidal precession, or perhaps by tidal
  decay.  The latter seems implausible on theoretical grounds, as it
  would require a stellar quality factor $Q_\star' \approx
  3\times10^4$.  Apsidal precession would imply an eccentricity
  $e\approx1.6\times 10^{-3}$, and the possibility of measuring the
  planet's Love number.  A Doppler shift from WASP-4's acceleration
  towards us could account for at most one quarter of the observed
  period change (at $2\sigma$).  Further observations will help
  confirm the reality of the timing variation, and eventually
  determine its cause.
\end{abstract}

>>>>

\title{WASP-4\lowercase{b} Arrived Early for the TESS Mission}

@@

\begin{abstract}
  %TODO: final numbers
  By combining data from the Transiting Exoplanet Survey Satellite (TESS)
  with data from previous studies, we show that the transit times of WASP-4b are
  incompatible with a constant orbital period.  The
  transits observed by TESS occurred $77.8 \pm 10.8$~seconds earlier than one would expect, based on the previous data.
  The orbital period appears to be shrinking by $\dot{P}=-12.1 \pm 1.2$
  milliseconds per year.   A simple clock offset is unlikely, because TESS observations of other
  hot Jupiter (WASP-6b, 18b, and 46b) are compatible with a constant period and rule out
  a 77.8-second offset at the 6.3$\sigma$ level.
  The timing variations seem to be astrophysical,
  and could be caused by apsidal precession, or perhaps by tidal
  decay.  The latter seems implausible on theoretical grounds, as it
  would require a stellar quality factor $Q_\star' \approx
  3\times10^4$.  Apsidal precession would imply an eccentricity
  $e\approx1.6\times 10^{-3}$, and the possibility of measuring the
  planet's Love number.  A Doppler shift from WASP-4's acceleration
  towards us could account for at most one quarter of the observed
  period change (at $2\sigma$).  Further observations will help
  confirm the reality of the timing variation, and eventually
  determine its cause.
\end{abstract}
